\section{Introduction}
\label{sec:introduction}

The rapid proliferation of shared electric scooters (e-scooters) has introduced a new class of urban safety challenge. Emergency department visits related to e-scooter injuries have surged globally, with head trauma and fractures dominating presentations \citep{trivedi2019injuries, bloom2021standing, badeau2019emergency}. Fatalities, though less frequent, often involve collisions with motor vehicles at speed \citep{yang2020safety}. The power model of the speed--crash relationship predicts that even modest speed increases lead to disproportionate injury risk---a relationship especially consequential for unprotected riders \citep{elvik2013reexamination}.

Recognizing this, jurisdictions worldwide have imposed regulatory speed limits on e-scooters: 25~km/h in South Korea and France, 20~km/h in Germany and the UK, and 15--25~km/h across US cities \citep{ma2021municipal, sexton2023shared}. In practice, compliance depends almost entirely on software-based speed governors embedded in the vehicle firmware, as traditional traffic enforcement rarely extends to e-scooters. Whether these governors effectively manage speed safety is therefore a central policy question.

Yet the question ``do speed governors reduce speeding?'' is largely tautological: a device that electronically caps maximum speed will, by design, prevent riders from exceeding the governed threshold. The more consequential---and empirically open---questions concern how speed governance reshapes riding behavior on \textit{unconstrained} margins. Speed is only one dimension of riding behavior; a governor constrains it mechanically, but leaves other behavioral margins free to adjust. Drawing on the behavioral economics framework of \citet{peltzman1975effects} and subsequent risk homeostasis literature \citep{wilde1982theory, hedlund2000risky}, we ask three questions: (1)~Do governed riders compensate through more aggressive acceleration, more erratic speed profiles, or altered riding dynamics? (2)~Does governance impose a demand cost---reducing trip frequency, shortening trips, or driving platform abandonment? (3)~Does the availability of an ungoverned ``fast option'' create a behavioral escalation pathway as riders gain experience?

Prior work has been constrained in three respects. First, existing studies analyze speed behavior through a single lens---typically binary threshold exceedance or spot-speed observations \citep{cicchino2023speed, ma2021escooter}---missing the multi-dimensional nature of riding behavior and conflating mechanical speed reduction with genuinely behavioral responses. Second, no study has provided \textit{causal} evidence on how speed governance affects behavioral outcomes beyond the governed threshold itself. Third, behavioral compensation (risk homeostasis) after governor policy changes has not been tested across multiple unconstrained margins, nor has the demand-side response---whether governance reduces ridership---been examined.

We address all three gaps using a uniquely comprehensive dataset. Swing, one of South Korea's largest shared e-scooter operators, offered three speed modes on identical hardware during 2023: TUB (turbo, ungoverned), STD (standard, governed to $\sim$25~km/h), and ECO (economy, governed to $\sim$20~km/h). Using 21 million GPS-instrumented trips with per-point sensor speed data from 52 cities over 10 months, we conduct a multi-outcome behavioral analysis across eight genuinely behavioral outcomes organized into three categories: safety (harsh acceleration, harsh deceleration, speed variability), demand (trip frequency, trip distance, user retention), and riding dynamics (cruising fraction, zero-speed fraction). Speed reduction itself is treated as a mechanical manipulation check---confirmed but not claimed as a finding. Our analytical framework comprises four blocks:

\begin{enumerate}
    \item \textbf{Cross-sectional behavioral profiles.} We characterize how safety, demand, and riding dynamics differ across operating modes using generalized estimating equations (GEE), within-subject paired comparisons, and SHAP-based feature importance from gradient-boosted tree models.

    \item \textbf{Multi-outcome causal identification.} In December 2023, Swing banned the ungoverned TUB mode system-wide. We exploit this exogenous shock in a multi-outcome difference-in-differences (DiD) framework with Bonferroni correction, estimating causal effects on each behavioral margin separately---identifying which margins respond to governance and which do not, including demand-side outcomes (trip counts, active users).

    \item \textbf{Behavioral compensation test.} We test whether riders compensate on \textit{any} unconstrained margin after losing access to the ungoverned mode, using within-user mode-switcher analysis with placebo validation across all eight outcomes.

    \item \textbf{Behavioral escalation pathway.} We analyze how ungoverned mode availability shapes behavior over time through experience--adoption mediation and survival analysis with multiple event types, including time-to-first-harsh-event and platform churn.
\end{enumerate}

To our knowledge, this is the first study to evaluate e-scooter speed governance effects on genuinely behavioral outcomes---beyond the tautological speed reduction---with causal identification. The multi-outcome framework maps a single policy lever (speed cap) onto multiple response margins (safety, demand, dynamics), providing a methodological template for evaluating speed management interventions that extends beyond binary compliance metrics.
