\documentclass[a4paper,fleqn]{cas-sc}

\usepackage[authoryear]{natbib}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\graphicspath{{figures/}{../../figures/}}
\usepackage{hyperref}
\usepackage{array}
\usepackage[pagewise]{lineno}

\linenumbers

\shorttitle{E-Scooter Speed Safety via City-Scale GPS Analysis}
\shortauthors{S.\ Choi}

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}

\title[mode=title]{Characterizing E-Scooter Riding Safety Through City-Scale Speed Profile Analysis}

\author[1]{Seongjin Choi}[orcid=0000-0001-7140-537X]
\ead{chois@umn.edu}
\cormark[1]
\credit{Conceptualization, Methodology, Formal analysis, Software, Writing -- Original Draft, Writing -- Review \& Editing, Supervision}

\address[1]{Department of Civil, Environmental, and Geo- Engineering, University of Minnesota, 500 Pillsbury Dr.\ SE, Minneapolis, MN 55455, USA}

\cortext[cor1]{Corresponding author}

\begin{abstract}
We present the first large-scale characterization of e-scooter speed behavior using 2.78 million GPS trajectories with per-point speed profiles from Swing, a major Korean operator, covering 52 cities and 382,328 users (May 2023), supplemented by 44.1 million trips over 24 months for longitudinal analysis. We find that 29.6\% of trips exceed the 25~km/h regulatory limit, but speeding is concentrated: 60.9\% of users never speed while 17.3\% speed on over half their trips. Spatial statistics (Getis-Ord $G_i^*$, Moran's $I$) identify significant speeding hotspots across five cities ($I = 0.16$--$0.71$, all $p < 0.001$). We estimate logistic regression with GEE, mixed-effects models, a two-part hurdle model, and a gradient-boosted tree with SHAP interpretability (AUC = 0.905) to disentangle rider demographics, operating mode, temporal context, and road infrastructure effects. The turbo (TUB) mode---which removes the software speed governor---dominates all models, increasing speeding odds 121-fold ($p < 0.001$) and SHAP importance (3.6$\times$ the next feature). A within-subject natural experiment ($n = 12{,}046$) confirms the governor reduces mean speed by 24\%, maximum speed by 31\%, and speeding from 7.4\% to 0.38\% (Cohen's $d = 1.0$--$2.2$). Longitudinal GEE analysis reveals monotonically increasing speeding with experience (3.8\% first trip to 28.0\% after 500+ trips; OR = 1.18 per doubling), driven by progressive TUB mode adoption rather than within-mode changes. A curvature analysis reveals a risk paradox: curvy roads have lower speeding prevalence but 5$\times$ higher risk scores when speeding occurs. Our findings support mandatory speed governors, targeted geofencing, and graduated mode access for new riders.
\end{abstract}

\begin{keywords}
e-scooter safety \sep speed behavior \sep GPS trajectory analysis \sep speed governor \sep spatial hotspot analysis \sep SHAP interpretability \sep micromobility regulation
\end{keywords}

\begin{highlights}
\item Analysis of 2.78M e-scooter trips with speed profiles across 52 Korean cities
\item Speed governor removal increases speeding odds 121-fold (OR = 121)
\item Rider experience increases speeding via progressive TUB mode adoption
\item SHAP analysis (AUC=0.905) validates TUB mode as dominant predictor
\item Curvy roads: lower speeding prevalence but 5x higher risk scores
\end{highlights}

\maketitle

\input{introduction}
\input{literature_review}
\input{data_description}
\input{methodology}
\input{results}
\input{discussion}
\input{conclusions}

\input{appendix}

\section*{Acknowledgments}
The authors thank Swing for providing the trip-level and trajectory datasets used in this study. All data were anonymized and used in accordance with the data sharing agreement. [Additional acknowledgments to be added.]

\section*{Author Contributions}
\textbf{Seongjin Choi}: Conceptualization, Methodology, Formal analysis, Software, Writing -- Original Draft, Writing -- Review \& Editing, Supervision. [Additional authors and contributions to be added.]

\section*{Data Availability}
The data used in this study were provided by Swing under a data sharing agreement and cannot be publicly shared due to privacy restrictions. The analysis code is available from the corresponding author upon reasonable request.

\bibliographystyle{cas-model2-names}
\bibliography{references}

\end{document}
