\documentclass[a4paper,fleqn]{cas-sc}

\usepackage[authoryear]{natbib}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\graphicspath{{figures/}{../../figures/}}
\usepackage{hyperref}
\usepackage{array}
\usepackage{multirow}
\usepackage[pagewise]{lineno}

\linenumbers

\shorttitle{Predict Then Verify: Behavioral Profiles Forecast Governance Effects}
\shortauthors{S.\ Choi}

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}

% Working title — to be finalized after results
% Candidates:
%   A: Predict Then Verify: Cross-Sectional Behavioral Profiles Forecast Speed Governance Effects
%   B: Behavioral Responses to E-Scooter Speed Governance: Multi-Outcome Evidence from 21 Million Trips
%   C: One Lever, Many Margins: How Speed Governance Reshapes E-Scooter Riding Behavior
\title[mode=title]{Predict Then Verify: Cross-Sectional Behavioral Profiles Forecast Speed Governance Effects Across 21 Million E-Scooter Trips}

\author[1]{Seongjin Choi}[orcid=0000-0001-7140-537X]
\ead{chois@umn.edu}
\cormark[1]
\credit{Conceptualization, Methodology, Formal analysis, Software, Writing -- Original Draft, Writing -- Review \& Editing, Supervision}

\address[1]{Department of Civil, Environmental, and Geo- Engineering, University of Minnesota, 500 Pillsbury Dr.\ SE, Minneapolis, MN 55455, USA}

\cortext[cor1]{Corresponding author}

\begin{abstract}
Software speed governors are the most widely deployed technological countermeasure for e-scooter speeding, yet asking whether they ``reduce speeding'' is tautological---a device that electronically caps speed mechanically prevents threshold exceedance by design. The more consequential questions concern whether governance reshapes riding behavior on \textit{unconstrained} margins: do riders compensate through more aggressive acceleration, more erratic speed profiles, or altered trip patterns? Does governance reduce ridership or cause platform abandonment? We develop a \textit{predict-then-validate} framework using 21 million GPS-instrumented e-scooter trips from 52 South Korean cities, analyzing eight genuinely behavioral outcomes across safety (harsh events, speed variability), demand (trip frequency, user retention), and riding dynamics (cruising, zero-speed fraction)---while treating speed reduction as a mechanical manipulation check. In Phase~I, cross-sectional analysis of three concurrent speed modes on identical hardware (February--November 2023) generates six testable predictions about which behavioral margins will respond to governance and which will not. In Phase~II, a natural experiment---the operator's system-wide removal of the ungoverned mode in December 2023---validates each prediction via multi-outcome difference-in-differences with Bonferroni correction, within-user compensation testing, and dose-response analysis. All six predictions are confirmed: harsh acceleration and deceleration respond causally to governance (safety margins), while speed variability, cruising patterns, trip counts, and user retention do not (demand and dynamics margins). Zero behavioral compensation is detected on any unconstrained margin. Cross-sectional behavioral profiling accurately forecasts causal governance effects, establishing a methodological template for pre-implementation assessment of speed management policies.
\end{abstract}

\begin{keywords}
e-scooter safety \sep speed governance \sep predict-then-validate \sep multi-outcome difference-in-differences \sep behavioral compensation \sep cross-sectional prediction
\end{keywords}

\begin{highlights}
\item Predict-then-validate framework: cross-sectional behavioral profiles generate testable predictions validated by natural experiment
\item Six predictions about governance effects on safety, demand, and dynamics margins---all six confirmed causally
\item Multi-outcome difference-in-differences with Bonferroni correction identifies selective response: safety margins respond, demand and dynamics do not
\item Within-user compensation test on all unconstrained margins yields zero behavioral compensation ($|d| < 0.14$)
\item Cross-sectional profiling shown to forecast causal policy outcomes---a template for pre-implementation assessment
\end{highlights}

\maketitle

\input{introduction}
\input{background}
\input{data_description}
\input{methodology}
\input{results}
\input{discussion}
\input{conclusions}

\input{appendix}

\section*{Acknowledgments}
The authors thank Swing for providing the trip-level and trajectory datasets used in this study. All data were anonymized and used in accordance with the data sharing agreement.

\section*{Author Contributions}
\textbf{Seongjin Choi}: Conceptualization, Methodology, Formal analysis, Software, Writing -- Original Draft, Writing -- Review \& Editing, Supervision.

\section*{Data Availability}
The data used in this study were provided by Swing under a data sharing agreement and cannot be publicly shared due to privacy restrictions. The analysis code is available from the corresponding author upon reasonable request.

\bibliographystyle{cas-model2-names}
\bibliography{references}

\end{document}
